FAIR theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2025-01-14 dk_example/example.tex
empty lines
add to dk example

With $-$ signifying a negative association and $\simeq$ meaning measured by.

@@

\section{Mathematical Formulation}

\section{(Statistical) Models}

\subsection{Correction}
There are different ways to correct for the bias introduced by measurement error:
\begin{itemize}
 \item use different test performances to calculate skill and overconfidence, but a small test-retest correlation can bias the estimate towrds zero then (Krueger and Mueller, 2002)
\end{itemize}

@@

>>>>

With $-$ signifying a negative association and $\simeq$ signifying measured by.

@@

\section{Mathematical Formulation}
Define random variables
\begin{itemize}
 \item $s^*$ denoting skill
 \item $\epsilon$ denoting measurement error, with $\Exp[\epsilon] = 0$, $\epsilon$ independent of all other random variables included in the model
 \item $s^*_s$ denoting self-assessed skill
\end{itemize}

\noindent Then we define performance $p$ as
\begin{equation} \label{p}
  p \coloneq s^* + \epsilon
\end{equation}
and overconfidence $oc^*$ as
\begin{equation} \label{oc}
  oc^* \coloneq s^*_s-s^*
\end{equation}
and expected performance $p_e$ as
\begin{equation} \label{ep}
  p_e \coloneq s^* + oc^*
\end{equation}
Overconfidence $oc^*$ is measured by overestimation $oe$ defined as
\begin{equation}
  oe \coloneq p_e - p
\end{equation}

\noindent From eq. \ref{oc} and \ref{ep} it follows that $p_e = s^*_s$ and further from eq. \ref{ep} and \ref{p} we see
\begin{align}
  oe &= p_e - p \\
  &= (s^* + oc^*) - (s^* + \epsilon) \\
  &= oc^* - \epsilon
\end{align}
\section{(Statistical) Models}

\subsection{Correction}
There are different ways to correct for the bias introduced by measurement error:
\begin{itemize}
 \item use different test performances to calculate skill and overconfidence, but a small test-retest correlation can bias the estimate towards zero then (Krueger and Mueller, 2002)
\end{itemize}

\section{Common Experimental Paradigm}
\begin{itemize}
 \item participants take a test
 \item participants guess their test performance either before or after the test
 \item bottom quartile performers vastly overestimate their performance, while top quartile performers access their performance more accurately
\end{itemize}

There are many replications for different populations and different tasks.

@@

\section{Notes}
\begin{itemize}
 \item difference in metacognitive skills drives the relationship between skill and overconfidence
\end{itemize}
